Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-16 TACAS2018/paper.tex
more comments

Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restrict the observability of the statespace from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}

>>>>

\todo{we are interested in observable systems so this is the definitely the case...}
Furthermore, a control system may have a derived
output that is a linear combination of its states and inputs, which may
restrict the observability of the state-space from the output space.
\begin{equation}
\label{eq:ode2}  
\vec{y}(t)=\mat{C}\vec{x}(t)+\mat{D}\vec{u}(t)
\end{equation}
